\section{Related Work}

\subsection{Slovene language resources and social-media corpora}

Written standard Slovene is well served by reference resources. Gigafida 2.0 \parencite{krek2020b-gf,gigafida-clarin} is the main reference corpus, with about 1.1 billion words of newspaper, web, and book text; ssj500k \parencite{krek2020a-ssj500k} provides manually annotated training data; siParl 3.0 \parencite{parliamentaryCorpus} covers parliamentary proceedings from 1990 to 2022. The broader methodological context is surveyed in \textcite{studije2005korpusnem}.

The most directly relevant prior work is the JANES project (\textit{Jezikovna analiza nestandardne slovenščine}), a central Slovene resource for computer-mediated communication, drawing primarily on Twitter but also covering news comments and forum posts \parencite{erjavec2019janes}. JANES mapped out much of the territory: the feasibility of building Slovene social-media corpora and the specific challenges they pose, including non-standard spelling, code-switching, short texts, and unreliable platform language tags. The present work is much smaller in scale and ambition; it revisits some of the same questions in the context of Bluesky.

\subsection{Bluesky and ATProto}

Prior work characterises Bluesky as both Twitter-like and decentralised, and links parts of its early growth to events around Twitter/X \parencite{failla2024bluesky,quelle2025bluesky}. The present corpus cannot establish why individual Slovene users joined Bluesky, but the late-2024 surge visible in Section~\ref{sec:empirical} is temporally compatible with that broader migration context.

Technically, Bluesky is built on the AT Protocol (ATProto), a federated specification that separates identity from hosting: user identities are DIDs (decentralised identifiers), and public records are stored in per-account repositories on Personal Data Servers \parencite{atproto-spec,atproto-repository}. ATProto also provides public synchronisation mechanisms: repository exports and a repository event stream, commonly called the firehose \parencite{atproto-sync,atproto-streaming}. From a corpus-collection standpoint, this means that public posts can be collected through protocol-level mechanisms rather than through a separate academic access programme. DID resolution allows a collector to follow an account regardless of which PDS hosts it, a property exploited by the multi-PDS collection approach described in this paper.

Existing empirical work on Bluesky has so far operated at large scale and focused primarily on platform-wide or network-level phenomena: \textcite{failla2024bluesky} assembled a dataset of about 235 million posts from over four million users for behavioural analysis, while \textcite{quelle2025bluesky} used Bluesky data to characterise network topology and political polarisation. To the author's knowledge, language-specific corpus construction for a smaller community on ATProto has not yet been reported in the literature.

\subsection{Language identification in corpus construction}

Building a language-specific corpus from a multilingual stream typically combines two signals: platform-supplied language metadata and automatic language identification. Neither is reliable on its own. Bluesky posts may contain a \texttt{langs} field with one or more BCP-47 language codes, and the official client auto-detects post languages while allowing users to override them \parencite{bsky-posts}. In the present corpus, 41.4\% of posts carry both \texttt{sl} and \texttt{en} tags, while langid assigns English to only 278 posts. This mismatch is one reason to treat platform language tags as useful metadata rather than ground truth. Automatic language identification tools---langid.py \parencite{lui2012langid} and langdetect \parencite{nakatani2010langdetect} are used here---are also imperfect, especially for short texts and closely related South Slavic languages. Using consensus across multiple detectors and requiring agreement with author-supplied tags improves precision, which is the rationale for the tiered inclusion strategy described in Section~\ref{sec:corpus-construction}.
