\section{Discussion}

The empirical findings in the previous section can be read in two ways: as descriptive statistics about a dataset, or as a portrait of a community caught in the process of forming. This section takes the second reading.

\subsection{A community with a visible history}

Most corpora are static snapshots --- the social processes that produced them are invisible in the data. This corpus is unusual in that its own growth structure records a visible transition. The near-zero activity before November 2024 and the 193-fold increase in that month mark the clearest structural break in the corpus. A majority of authors first appear in the corpus in November or December 2024, while lower-volume activity is already present from August 2023 onward.

This matters for how the corpus is interpreted. The language in it was produced under specific social conditions: during a period of platform disruption, by people establishing or re-establishing an online presence in a small public space. Whether these conditions leave traces in the language is an open question.

\subsection{Dialogue over broadcasting}

The most striking single finding is the reply rate: 68.3\% of all posts are replies, with original posts accounting for 29.4\% and non-reply quote posts for 2.3\%. This distribution points to use centred more on exchange than on broadcasting.

The author-level evidence points in the same direction. Among the 246 authors with at least 20 posts in the corpus, the median per-author reply rate is 0.66, and only 9 (3.7\%) have a reply rate of zero. A robustness check confirms that the median monthly reply share is nearly identical in the full corpus and in this active-author subset (67.1\% vs.\ 67.3\%), suggesting that the conversational character of the corpus is not an artefact of marginal one-off contributors. Using simple descriptive thresholds, most active authors fall into a mixed or strongly conversational group; the broadcast-heavy group (reply rate below 0.2) accounts for a small minority of authors and posts. These groupings are heuristic rather than validated social categories, but they help frame the distribution.

Notably, this pattern is not a product of the late-2024 influx of new authors. Before November 2024, replies already accounted for 54.5\% of posts in the corpus. The post-surge growth is therefore consistent with a continuation and strengthening of an interactional tendency that was already present, rather than a shift in the kind of activity taking place. Whether this reflects the small-community character of the corpus, platform affordances, or the particular interests of early adopters cannot be established from these data alone.

\subsection{Small but coherent}

The Slovene Bluesky community captured here is small by the standards of any major language platform, and participation is concentrated around a core group of highly active users. The hashtag and linking patterns make that public space easier to describe more precisely.

Hashtag use is sparse (4.9\% of posts) and largely concentrated in individual accounts: 18 of the 20 most frequent hashtags have a single author contributing more than half of all uses. This is consistent with a space that is not organised around broad hashtag-driven topic publics. It is also consistent with the conversational register identified in Section~\ref{sec:interactional}: when interaction is primarily dialogic, hashtags function less as thematic coordination devices and more as occasional self-tagging or platform-cultural signals.

Linking practices tell a complementary story. External domains appear in 12.6\% of posts, more than twice the hashtag rate. The linked content is shaped primarily by Slovene news media (35.8\% of domain occurrences), GIF and media-sharing services (14.5\%), and Bluesky-native tooling (11.2\%), with video platforms (8.0\%) also prominent. The news-media linking is distributed across several outlets, suggesting recurring current-affairs engagement rather than dependence on a single source. GIF sharing, by contrast, is a broadly shared informal practice: \texttt{media.tenor.com} alone appears in posts by 121 different authors.

Taken as a whole, the hashtag and linking patterns point to a small conversational public space oriented around informal exchange, recurring news-media engagement, and platform-native practices --- rather than a thematically organised mass public. The daily rhythm consistent with Slovenian working hours reinforces this portrait of a geographically and linguistically bounded community, though the corpus size makes finer-grained claims about internal subgroups difficult to support.

\subsection{ATProto as a research infrastructure}

From a methodological standpoint, the experience of building this corpus confirms that ATProto's open design has real consequences for research. Public synchronisation and repository mechanisms made a backfill of the discovered Slovene-linked authors achievable without special research access \parencite{atproto-sync,atproto-streaming}. For researchers working on small or under-resourced languages --- where corpora are scarce and institutional resources are limited --- this openness matters. The Slovene community on Bluesky may be small, but it is unusually well documented as a result.
