\section{Conclusion}

This paper has presented a reproducible workflow for building a high-precision corpus of public Slovene Bluesky posts and used that corpus for an initial analysis of interaction and multilinguality on the platform.

The methodological contribution is a multi-stage pipeline that combines network-wide tagged discovery (both historical crawl and live firehose), DID-based full-history backfill from individual Personal Data Servers, and conservative post-level language filtering validated through manual annotation. The pipeline is fully protocol-native: it requires no API keys, no institutional data-access agreements, and no reliance on a single centralised server. For small-language communities where research infrastructure is limited, this openness is a meaningful practical advantage.

The empirical contribution is a first portrait of Slovene Bluesky use. The corpus of 141,013 posts by 432 authors reveals a community whose recoverable activity expands sharply in late 2024, is dominated by dialogue rather than broadcasting, and is concentrated around a small core of highly active users. The presence of identifiable subgroups (a paddleboarding community, several news organisations), a clear Slovenian-timezone daily rhythm, and a small but non-trivial set of users on independent infrastructure all suggest that this is not a random collection of accounts but a community with genuine internal structure.

The corpus should be understood as a snapshot of currently recoverable public posts from discovered Slovene-linked authors, not a complete census of all Slovene writing on Bluesky. Deleted posts are excluded, and within the pool of excluded untagged posts from known authors that meet the project's minimum-text rule, the false-negative rate is estimated at approximately 8.5\%. Future work could extend the corpus longitudinally, apply the same methodology to other small languages on the ATProto network, or use the corpus as a basis for NLP tasks such as non-standard Slovene processing, sentiment analysis, or community detection. Linguistic annotation --- morphosyntactic tagging, lemmatisation, and normalisation of non-standard forms --- would be a natural next step, following the approach established by the JANES project for Slovene user-generated content.
